### 2019-03-18 papers/journal/encoding.tex
update in bmc:09

Our first attempt was to encode the existential condition check as a $\fbmc$ search problem.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is not considerably different.
% 
The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
%
Hence, we will only present the stability encoding.  
%
Rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.

In the $\fbmc$ encoding, the label of the edges and nodes are represented by variables of type arrays of bit vector of size $M$. 
%
For example, the variable \texttt{bvEdge}$[i][j][q]$, represent the label of the $q$th edge between node $i$ and $j$.

>>>>

Our first attempt was to encode the existential condition check as a $\fbmc$ search problem.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is not considerably different.
% 
The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
%
Here, we will only present the stability encoding.
%the rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.

In the $\fbmc$ encoding, the label of the edges and nodes are represented by variables of type, \textit{array of bit vector} of size $M$. 
%
For example, the variable \texttt{bvEdge}$[i][j][q]$, represent the label of the $q$th edge between node $i$ and $j$.
